%!TEX TS-program = xelatex
\documentclass[a4paper,online]{adcv}

\usepackage[english]{babel}

\newcommand*{\hib}{Abbey College Manchester}
\newcommand*{\uib}{University of Salford}
\newcommand*{\uniaq}{Universit{\`a} degli Studi dell’Aquila}

\addbibresource{bib_alessandro_rossini.bib}

\title{Haashim Alvi’s CV}

\adcvname{Haashim}{Alvi}{BSc}
\adcvtitle{Network Engineer, Systems Tester, Teaching Assistant}
\adcvaddress{15 Manley Road}{}{Manchester}{England}
\adcvwebsite{https://alessandrorossini.org}{linkedin.com/in/haashim-alvi}
\adcvemail{haashimalvi}{pm}{me}
\adcvphone{(+44) 7450 281801}
\adcvdate{Nov 2020}

\begin{document}

\section{Personal Statement}\label{sec:personal statement}

I have always been interested in how technology works and is designed, as well as how it can be improved. This interest led me to experiment with different types of technology looking for functionality and features that weren’t intended by the developers and sharing them with friends. As I learned more about computers, friends and family were interested in learning about them, so I helped teach them. These skills helped me learn about how to be a friendly approachable person as well as a good leader. I proved this by leading and communicate between different people for group projects. I’m also currently the Treasurer of the Computing Society of Salford. This role has helped me learn about how to organize and promote events. During these events I have met people from a wide range of backgrounds and learned about what they think of computing and programming. This gave me a better understanding of the common misconceptions about computing and has helped me make good friends.

\section{Experience}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Teaching Assistant}, Salford College, Manchester, Greater Manchester}{2020--Present}
  \adcvrowmulti{A work placement that involves experience in the Further Education sector. I'm currently shadowing teachers and planning lessons virtually, whilst attending meetings with senior teachers going through tutorials on what's required for being an effective teacher. This role has allowed me to improve my interpersonal skills, by communicating regularly with teachers about the opinions. This has helped me change my overall perception of teaching and improve my confidence in the subjects I'm assisting with. }
  \adcvrowskip
   \adcvrowtwo{\textbf{Campus Steward}, University of Salford, Manchester, Greater Manchester}{2020}
     \adcvrowskip
  \adcvrowtwo{\textbf{Systems Tester}, Skipton Building Society, Skipton, North Yorkshire}{2019--2020}
  \adcvrowmulti{Completed my internship at SBS, which involved internal testing of software used by the society. I was tasked with accurately testing systems, as well as performing analysis on business requirements. I would document my outputs, record results, identify defects, and communicate these back to the software developers so they can be fixed. The role gave me the opportunity to write my own testing guide for regulatory software that I had tested. The rest of the team weren’t as confident in the testing of the software, so I provided a breakdown of the testing procedure in order to ensure that it could be easily understood.}
  \adcvrowskip
  \adcvrowtwo{\textbf{Network Engineer}, R.A.S Ltd, Rochdale, Greater Manchester}{2018}
  \ifextended
    \adcvrowmulti{Upgraded the DOS based legacy system with slow networking speeds, to one which uses NAS for live data storage giving users access to data using an ISCSI based system. This data is regularly imaged and backed up to an offsite location. This approach gave me greater control on the access rights of the data for different users.~(see \hyperref[sec:supervision]{Supervision} below).}
  \else
    \adcvrowmulti{Upgraded the DOS based legacy system with slow networking speeds, to one which uses NAS for live data storage giving users access to data using an ISCSI based system. This data is regularly imaged and backed up to an offsite location. This approach gave me greater control on the access rights of the data for different user.}
  \fi
  \adcvrowskip
\end{adcvtabletwo}
\section{Projects}\label{sec:projects}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Smart Meter Project}, Joule House, University of Salford}{Nov 2018-- Feb 2019}
  \adcvrowmulti{The Norwegian Directorate of eHealth established the Health Data Program for contributing to better health research and more knowledge-based health services through better utilization and quality of Norwegian health data. This program is developing the Health Analytics Platform, which consists of a data platform with copies of data from the country’s health registries, along with an ecosystem of analytics tools.}
  \adcvrowmulti{As \textbf{Subject Matter Expert}, Alessandro has been responsible for: estimating fixed and variable costs for the operation of the Health Analytics Platform; identifying technical and commercial measures for cost reduction; defining financing and governance models for the operation of the Health Analytics Platform.}
  \ifextended
    \adcvrowskip
  \else
    \newpage
  \fi
  \adcvrowtwo{\textbf{Operation and Development Platform}, The Norwegian Tax Administration}{2018--2020}
  \adcvrowmulti{The Norwegian Tax Administration established a set of strategic measures in IT to put the organization in the best possible position to develop, manage, and operate IT services. One of these measures was to assess the cloud as the primary operation and development platform for the Norwegian Tax Administration.}
  \adcvrowmulti{As \textbf{Subject Matter Expert} and \textbf{Project Manager}, Alessandro contributed to: defining a strategy, governance model, learning plan, and target architecture; establishing a framework agreement for cloud services and evaluating offers from the market; charting and assessing applications, platform, and infrastructure; cost analysis of platform and infrastructure on-premises; cost estimation of migrating to public cloud and collaboration platforms; establishing a framework for cost categorization based on Technology Business Management.}
  \adcvrowskip
  \adcvrowtwo{\textbf{Technical Due Diligences}, multiple private companies}{2019--2020}
  \adcvrowmulti{A technology due diligence (Tech DD) offers an independent evaluation of the technology in an enterprise, often in the context of mergers and acquisitions. PwC has performed Tech DDs for private companies in the services, IT, energy, oil and gas, maritime, and real estate sectors.}
  \adcvrowmulti{As \textbf{Subject Matter Expert}, Alessandro has been responsible for assessing strengths, weaknesses, and red flags within: digital strategy, roadmap and portfolio; IT organization; IT governance and sourcing; architecture and technology stack; cloud, infrastructure and platform; insights and automation; cyber security.}
  \adcvrowskip
  \adcvrowtwo{\textbf{Cloud Management Platform}, EVRY}{2017--2018}
  \ifextended
    \adcvrowmulti{EVRY (now TietoEVRY) built a cloud management platform for comparing, purchasing and orchestrating services in a hybrid cloud.}
    \adcvrowmulti{As \textbf{Subject Matter Expert} and \textbf{Architect}, Alessandro was responsible for: market analysis; requirement specification; architecture design based on the state-of-the-art in research and development; interaction with third party vendors.}
  \fi
  \adcvrowskip
  \adcvrowtwo{\textbf{\href{https://cordis.europa.eu/project/id/645372}{ARCADIA}}, European Commission’s H2020 Programme}{2014--2016}
  \ifextended
    \adcvrowmulti{A framework for developing highly distributed applications. Rated Excellent by the European Commission.}
    \adcvrowmulti{Alessandro was Leader of the Task on Context Models, and Project Manager at SINTEF.}
  \fi
  \adcvrowskip
  \adcvrowtwo{\textbf{\href{https://paasage.ercim.eu}{PaaSage}}, European Commission’s 7$^{\mbox{\scriptsize th}}$ Framework Programme}{2012--2016}
  \ifextended
    \adcvrowmulti{A model-based framework for specifying and executing cross-cloud applications. Rated Excellent by the European Commission.}
    \adcvrowmulti{Alessandro was Leader of the Work Package on Languages, and Project Manager at SINTEF.}
  \fi
  \adcvrowskip
  \adcvrowtwo{\textbf{\href{https://sites.google.com/site/brokeratcloud/}{Broker@Cloud}}, European Commission’s 7$^{\mbox{\scriptsize th}}$ Framework Programme}{2012--2016}
  \ifextended
    \adcvrowmulti{A cloud brokerage framework for quality assurance and optimization.}
    \adcvrowmulti{Alessandro was Leader of the Task on Cloud Service Failure Prevention and Recovery, and Project Manager at SINTEF.}
  \fi
  \adcvrowskip
  \adcvrowtwo{\textbf{\href{https://ict.hvl.no/dpf/}{DPF}}, \uib{} and \hib{}}{2008--2012}
  \ifextended
    \adcvrowmulti{A diagrammatic specification framework founded on category theory.}
    \adcvrowmulti{Alessandro was Researcher and Quality Assurance Manager.}
  \fi
  \adcvrowskip
  \adcvrowtwo{\textbf{\href{http://zeronotice.org}{ZNF}}, Self-funded}{2005--2007}
  \ifextended
    \adcvrowmulti{An open source framework for developing enterprise web applications.}
    \adcvrowmulti{Alessandro was Project Manager and Chief Architect.}
  \fi
\end{adcvtabletwo}

\ifextended
  \section{Committees}\label{sec:committees}

  \textbf{Organizing Committee Member}: \href{https://doi.org/10.1007/978-3-319-19249-9}{FM 2015}, \href{https://doi.org/10.1007/978-3-319-14886-1}{CSB 2014}, \href{https://doi.org/10.1145/2513534.2513535}{NordiCloud 2013}

  \textbf{Program Committee Member}: \href{https://www.conf-micro.services/2019/}{Microservices 2019}, \href{http://ceur-ws.org/Vol-2336/}{MMHS 2018}, \href{https://www.wi-inf.uni-duisburg-essen.de/MULTI2018/}{MULTI 2018}, \href{https://sites.google.com/site/cloudwaysws18/}{CloudWays 2017}, \href{https://doi.org/10.1007/978-3-319-99819-0}{ESOCC 2018}, \href{http://www.se-cloud.scitevents.org/}{SE-CLOUD 2018}, \href{https://sites.google.com/site/cloudways17/}{CloudWays 2017}, \href{https://doi.org/10.1007/978-3-319-67262-5}{ESOCC 2017}, \href{https://swt4.informatik.uni-mannheim.de/multi-2016/}{MULTI 2016}, MMHS 2016, \href{http://procon-workshop.com/}{PROCON 2016}, \href{https://doi.org/10.1007/978-3-319-44482-6}{ESOCC 2016}, \href{https://miso.es/multi/2015/}{MULTI 2015}, MMHS 2015, \href{https://miso.es/multi/2014/}{MULTI 2014}, MMHS 2014, \href{https://sites.google.com/site/cloudbrokerworkshop/}{CSB 2013}, \href{https://doi.org/10.1007/978-3-642-36089-3}{SLE 2012}

  \textbf{Reviewer}: \href{https://ees.elsevier.com/compeleceng/}{CAEE}, \href{https://www.springer.com/journal/10270}{SoSyM}, \href{https://www.springer.com/computer/journal/607}{Computing}, \href{https://nik.no/nik-2013/}{NIK 2013}, \href{https://doi.org/10.1007/978-3-642-41533-3}{MODELS 2013}, \href{https://onlinelibrary.wiley.com/journal/20477481}{JSME}, \href{https://doi.org/10.1007/978-3-642-33666-9}{MODELS 2012}, \href{https://doi.org/10.1007/978-3-642-31491-9}{ECMFA 2012}, \href{https://doi.org/10.1007/978-3-642-34176-2}{AGTIVE 2011}, \href{https://doi.org/10.1007/978-3-642-21732-6}{ICMT 2011}
\fi

\section{Education}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Bsc. Computer Science with Web Development}, Dep. of Informatics, \uib{}, Norway}{2011}
  \ifextended
    \adcvrowmulti{Subject of the dissertation: \href{https://hdl.handle.net/1956/5261}{Diagram Predicate Framework meets Model Versioning and Deep Metamodelling}.}
    \adcvrowmulti{Supervisors: \href{https://www.uib.no/persons/Uwe.Wolter}{Uwe Wolter} and \href{https://www.uib.no/en/persons/Khalid.Azim.Mughal}{Khalid Azim Mughal}. Opponents: \href{https://www.cs.le.ac.uk/people/rh122/}{Reiko Heckel} and \href{http://einarj.at.ifi.uio.no}{Einar Broch Johnsen}.}
  \fi
  \adcvrowskip
  \adcvrowtwo{\textbf{Master of Science (M.Sc.)}, Dep. of Computer Science, \uniaq{}, Italy}{2006}
  \ifextended
    \adcvrowmulti{Final grade: \textit{Summa cum laude}. Specialized curriculum in software engineering and web technology. One-year stay as Erasmus student at the Department of Informatics, \uib{}, Norway. Subject of the dissertation: Problems of Versioning in Model-Driven Architecture. Supervisor: \href{https://www.disim.univaq.it/main/home.php?users_username=alfonso}{Alfonso Pierantonio}.}
    \adcvrowskip
    \adcvrowtwo{\textbf{Bachelor of Science (B.Sc.)}, Dep. of Computer Science, \uniaq{}, Italy}{2003}
    \adcvrowmulti{Final grade: \textit{Summa cum laude}. General curriculum in computer science. Subject of the dissertation: Generation of Data-Intensive Web Applications Based on UML. Supervisor: \href{https://www.disim.univaq.it/main/home.php?users_username=alfonso}{Alfonso Pierantonio}.}
  \fi
\end{adcvtabletwo}

\section{Certifications}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{AWS Certified Cloud Practitioner}}{2020}
  \adcvrowskip
  \adcvrowtwo{\textbf{Azure Fundamentals}}{2020}
  \adcvrowskip
  \adcvrowtwo{\textbf{Certified Technology Business Management Executive (CTBME)}}{2020}
  \adcvrowskip
  \adcvrowtwo{\textbf{TOGAF 9 Foundation}}{2019}
  \adcvrowskip
  \adcvrowtwo{\textbf{PRINCE2 Agile Practitioner in Agile Project Management}}{2019}
  \ifextended
    \adcvrowskip
    \adcvrowtwo{\textbf{PRINCE2 Foundation in Project Management}}{2018}
  \fi
\end{adcvtabletwo}

\section{Courses}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Business Outcome Enablement}, Global Knowledge, Oslo, Norway}{2017}
  \adcvrowskip
  \ifextended
    \adcvrowtwo{\textbf{Project Management}, SINTEF School, Trondheim, Norway}{2014}
    \adcvrowskip
  \fi
  \adcvrowtwo{\textbf{Research Methodology}, SINTEF School, Trondheim, Norway}{2013}
  \adcvrowskip
  \adcvrowtwo{\textbf{LASER Summer School on Empirical Software Engineering}, ETH, Z{\"u}rich, Switzerland}{2010}
\end{adcvtabletwo}

\ifextended
  \section{Teaching}\label{sec:teaching}

  \begin{adcvtabletwo}
    \adcvrowtwo{\textbf{Lecturer}, Industrial Software Engineering (in Norwegian)}{Spring 2012}
    \adcvrowmulti{Bachelor course TOE058, \hib{}}
    \adcvrowskip
    \adcvrowtwo{\textbf{Teaching assistant}, Software Security (in English)}{Fall 2010}
    \adcvrowmulti{Master course INF226, \uib{}}
    \adcvrowskip
    \adcvrowtwo{\textbf{Teaching assistant}, Software Engineering (in Norwegian)}{Spring 2010}
    \adcvrowmulti{Bachelor course INF112, \uib{}}
    \newpage
    \adcvrowtwo{\textbf{Teaching assistant}, Software Engineering (in Norwegian)}{Spring 2009}
    \adcvrowmulti{Bachelor course INF112, \uib{}}
    \adcvrowskip
    \adcvrowtwo{\textbf{Teaching assistant}, Software Security (in English)}{Fall 2008}
    \adcvrowmulti{Master course INF226, \uib{}}
    \adcvrowskip
    \adcvrowtwo{\textbf{Teaching assistant}, Program Development Methodologies (in Norwegian)}{Spring 2008}
    \adcvrowmulti{Bachelor course INF101, \uib{}}
    \adcvrowskip
    \adcvrowtwo{\textbf{Trainer}, European Computer Driving License (ECDL)-like courses (in Italian)}{2004--2005}
    \adcvrowmulti{Computer Usage, File Management, Word Processing, Spreadsheets, and Databases}
  \end{adcvtabletwo}

  \section{Supervision}\label{sec:supervision}

  \begin{adcvtabletwo}
    \adcvrowtwo{\href{https://www.linkedin.com/in/jakob-høgenes-9a878b122/}{\textbf{Jakob Høgenes}}, Master student in Engineering Cybernetics, NTNU. Summer internship at SINTEF.}{2014}
    \adcvrowskip
    \adcvrowtwo{\href{https://www.linkedin.com/in/nikolay-nikolov-a9672659/}{\textbf{Nikolay Nikolov}}, International Master student in Service Engineering, Tilburg University, University of Stuttgart, and University of Crete. Master thesis at SINTEF.}{2014}
    \adcvrowskip
    \adcvrowtwo{\href{https://www.linkedin.com/in/tudor-domnița-a6b6b3a2/}{\textbf{Tudor Domnita}}, Bachelor student in Computer Science, Technical University of Cluj-Napoca. Summer internship at SINTEF.}{2013}
  \end{adcvtabletwo}
\fi

\section{Languages}

\ifextended
  \begin{adcvlanguages}
    \adcvmothertongue{Italian}
    \adcvlanguagesheader
    \adcvlanguage{2}{English}{\adcvCTwo}{\adcvCTwo}{\adcvCTwo}{\adcvCTwo}{\adcvCTwo}
    \adcvlanguage{3}{Norwegian (Bokmål)}{\adcvCTwo}{\adcvCTwo}{\adcvCTwo}{\adcvCTwo}{\adcvCTwo}
    \adcvlanguage{}{Spanish}{\adcvCOne}{\adcvCOne}{\adcvBTwo}{\adcvBTwo}{\adcvBTwo}
    \adcvlanguagesfooter
    \adcvlanguagesfootnote{2}{Course in Academic English at the \uib{}}
    \adcvlanguagesfootnote{3}{Bestått eksamen i norsk språk og kultur trinn 4 ved Uni. i Bergen, ekvivalent med Bergenstesten}
  \end{adcvlanguages}
\else
  \textbf{Italian}: Native proficiency

  \textbf{English}, \textbf{Norwegian}: Full professional proficiency

  \textbf{Spanish}: Limited working proficiency
\fi

\section{Personal interests}

Science, Technology, Traveling, Photography, Languages, Communication, Food, Wine, Movies, Music, Hiking

\section{Publications}

\ifextended
  \begin{refsection}
    \nocite{AichernigRossini15}
    \nocite{SimonsRossiniPJ14}
    \printbibliography[title={Books and edited proceedings}, heading=subbibliography]
  \end{refsection}

  \begin{refsection}
    \nocite{AchilleosKritikosRKDOSGNRP19}
    \nocite{BergmayrBreitenbucherFRSWKL18}
    \nocite{FerryChauvelSRLS18}
    \nocite{RossiniDeLaraGRW14}
    \nocite{RutleRossiniLW12}
    \nocite{RossiniRutleLW10}
    \printbibliography[title={Peer-reviewed journals}, heading=subbibliography]
  \end{refsection}

  \begin{refsection}
    \nocite{RossiniRutleLW18}
    \nocite{SeyboldDomaschkaRHGT16}
    \nocite{NikolovRossiniK15}
    \nocite{DomaschkaGriesingerBR15}
    \nocite{BergmayrRossiniFHOSW15}
    \nocite{Rossini16}
    \nocite{RossiniDeLaraGN15}
    \nocite{KritikosDomaschkaR14}
    \nocite{FerrySongRCS14}
    \nocite{SimonsBratanisKPVVMBR14}
    \nocite{VeloudisParaskakisVPR14}
    \nocite{DomaschkaKritikosR14}
    \nocite{FerryBrataasRCS14}
    \nocite{KourtesisBratanisFVSRSG14}
    \nocite{ChauvelFerryMRS13}
    \nocite{FerryChauvelRMS13}
    \nocite{FerryRossiniCMS13}
    \nocite{RossiniDeLaraGRL11}
    \nocite{MantzRossiniTLW11}
    \nocite{RossiniRutleMLW11}
    \nocite{SimonsenMantzRR10}
    \nocite{RossiniRutleMLW10}
    \nocite{MantzRossiniRLW10}
    \nocite{RossiniRutle10}
    \nocite{RutleRossiniLW10}
    \nocite{RutleRossiniLW09NWPT}
    \nocite{RossiniRutleMHMLW09}
    \nocite{RutleRossiniLW09TOOLS}
    \nocite{RutleRossiniLW09FASE}
    \nocite{RutleRossiniLW08NWPTMT}
    \nocite{RutleRossiniLW08NWPTVC}
    \nocite{RutleRossini08}
    \nocite{CicchettiRossini07}
    \printbibliography[title={Peer-reviewed conference proceedings}, heading=subbibliography]
  \end{refsection}

  \begin{refsection}
    \nocite{RossiniKritikosNDSGROKA17}
    \nocite{ARCADIAD31a}
    \nocite{BrokerAtCloudD404}
    \nocite{PaaSageD213}
    \nocite{ARCADIAD22}
    \nocite{BrokerAtCloudD402}
    \nocite{PaaSageD212}
    \nocite{PaaSageD211}
    \nocite{MODACloudsD41}
    \nocite{CicchettiRossini06}
    \printbibliography[title={Project deliverables and technical reports}, heading=subbibliography]
  \end{refsection}

  \begin{refsection}
    \nocite{Rossini20TU}
    \nocite{Rossini19DN}
    \nocite{Rossini19TU}
    \nocite{Rossini17Aftenposten}
    \nocite{Rossini11PaaHoeyden}
    \nocite{RossiniLiberati05}
    \printbibliography[title={Newspapers and magazines}, heading=subbibliography]
  \end{refsection}
\else
  \href{https://scholar.google.com/citations?user=s1bqnpoAAAAJ}{40+ publications} in peer-reviewed conference proceedings and journals.
\fi

\ifextended
  \section{Presentations}

  \begin{adcvpresentations}
    \adcvpresentation{\href{https://www.tekna.no/fag-og-nettverk/forskning-og-innovasjon/forskningsbloggen/bygge-bro-mellom-forskning-og-naeringsliv/}{Why academia is from Venus and industry from Mars}}{Tekna, Oslo, Norway, 29 Oct 2019}
    \adcvpresentation{Bridging the technological “valley of death”}{Norwegian University of Science and Technology, Trondheim, Norway, 6 Jun 2019}
    \adcvpresentation{Bridging the technological “valley of death”}{PhD Seminar, Western Norway University of Applied Sciences, Geilo, Norway, 29 Jan 2019}
    \adcvpresentation{Model-Driven Engineering and Cloud Management Platforms}{{Architecture group meeting, PwC Consulting}, Oslo, Norway, 27 Sep 2018}
    \adcvpresentation{What industry wants from academia}{ESOCC 2017, Oslo, Norway, 28 Sep 2017}
    \adcvpresentation{What industry wants from academia}{Western Norway University of Applied Sciences, Bergen, Norway, 12 Sep 2017}
    \adcvpresentation{Differences between academia and industry}{Scienza senza confini, Oslo, Norway, 12 May 2017}
    \adcvpresentation{The lessons I have learned in more than four years at SINTEF}{SINTEF, Oslo, Norway, 27 Feb 2017}
    \adcvpresentation{Model-Driven Engineering of Cloud Applications}{Future of Clouds, Budapest, Hungary, 27 Sep 2016}
    \adcvpresentation{Cloud Application Modelling with CAMEL}{PaaSage Industrial Workshop at EVRY, Oslo, Norway, 20 Sep 2016}
    \adcvpresentation{\href{https://alessandrorossini.org/no-email-not-collaborative-editing-solution-comparison-state-of-the-art/}{No, email is not a collaborative editing solution---A comparison of the state-of-the-art}}{SINTEF, Oslo, Norway, 2 Jun 2016}
    \adcvpresentation{Cloud Application Modelling and Execution Language (CAMEL)}{From Cloud to Road, Stuttgart, Germany, 11 Apr 2016}
    \adcvpresentation{\href{https://alessandrorossini.org/chocolate-hazelnut-spread-experiment/}{The Chocolate-Hazelnut Spread Experiment}}{SINTEF, Oslo, Norway, 10 Mar 2016}
    \adcvpresentation{Big Data Meets Cloud}{Big Data Meets Cloud SINTEF seminar, Oslo, Norway, 20 Oct 2015}
    \adcvpresentation{Failure Prevention and Recovery (FPR) Mechanism, part of the Broker@Cloud Tutorial}{ESOCC 2015, Taormina, Italy, 17 Sep 2015}
    \adcvpresentation{Cloud Application Modelling and Execution Language (CAMEL) and the PaaSage Workflow}{ESOCC 2015, Taormina, Italy, 15 Sep 2015}
    \adcvpresentation{A Comparison of Two-Level and Multi-Level Modelling for Cloud-Based Applications}{ECMFA 2015, part of STAF 2015, L’Aquila, Italy, 23 Jul 2015}
    \adcvpresentation{Failure Analysis, Prevention, and Recovery}{\uib and \hib, Norway, 28-29 Apr 2015}
    \adcvpresentation{Self-Adaptive Multi-Cloud Applications}{\uib and \hib, Norway, 28-29 Apr 2015}
    \adcvpresentation{PaaSage---Modelling and Execution of Multi-Cloud Applications}{SeaClouds 2014, Manchester, UK, 2 Sep 2014}
    \adcvpresentation{Cloud Modelling Language}{University of Oslo, Norway, 6 May 2013, 24 May 2014}
    \adcvpresentation{Self-Adaptive Cloud-Based Applications}{Future Internet Assembly 2014, Athens, Greece, 17 Mar 2014}
    \adcvpresentation{Broker@Cloud---Continuous Quality Assurance and Optimisation for Cloud Brokers}{NordiCloud 2013, Oslo, Norway, 2 Sep 2013}
    \adcvpresentation{Towards Model-Driven Provisioning, Deployment, Monitoring, and Adaptation of Multi-Cloud Systems}{Advanced School on Service Oriented Computing, Hersonissos, Greece, 4 Jul 2013}
    \adcvpresentation{Towards Model-Driven Provisioning, Deployment, Monitoring, and Adaptation of Multi-Cloud Systems}{IEEE CLOUD 2013, Santa Clara, CA, USA, 30 Jun 2013}
    \adcvpresentation{Computer Science and Society: Is a New Social Contract Possible?}{\uib, Norway, 2 Oct 2012, 1 Feb 2012, 26 Sep 2011, 31 Jan 2011, 29 Sep 2010, 2 Feb 2010, 22 Sep 2009, 4 Feb 2009}
    \adcvpresentation{Model Versioning and Multi-Level Modelling}{SINTEF, Oslo, Norway, 24 Sep 2012}
    \adcvpresentation{Model Versioning and Multi-Level Modelling}{Aalesund University College, Ålesund, Norway, 21 Sep 2012}
    \adcvpresentation{A Graph Transformation-Based Semantics for Deep Metamodelling}{AGTIVE 2011, Budapest, Hungary, 5 Oct 2011}
    \adcvpresentation{A Formal Approach to Data Validation Constraints in MDE}{TTSS 2011, Oslo, Norway, 13 Sep 2011}
    \adcvpresentation{Action plan for PhD-education at the Faculty of Mathematics and Natural Sciences. PhD gathering of the Department of Mathematics}{\uib, Norway, 25 Nov 2010}
    \adcvpresentation{Constraint-Aware Model Merging}{NWPT 2010, Turku, Finland, 11 Nov 2010}
    \adcvpresentation{PhD panel at the Faculty of Mathematics and Natural Sciences. PhD seminar of the Department of Biology}{\uib, Norway, 19 Oct 2010}
    \adcvpresentation{Data Validation Constraints in MDE}{NWPT 2009, Lingby, Denmark, 16 Oct 2009}
    \adcvpresentation{A Category-Theoretical Approach to the Formalisation of Version Control in MDE}{FASE 2009, York, UK, 25 Mar 2009}
    \adcvpresentation{Version Control in MDE}{NWPT 2008, Tallinn, Estonia, 20 Nov 2008}
    \adcvpresentation{Free software and open source}{Università degli Studi di Urbino, Italy, 13 Apr 2005}
    \adcvpresentation{Kernel tuning}{LinuxDay 2004, L’Aquila, Italy, 27 Nov 2004}
    \adcvpresentation{GNU/Linux: a window to the future}{Festa dell’unità 2004, L’Aquila, Italy, 13 Jul 2004}
    \adcvpresentation{Hardening the box}{Seminari 2004 OpenLUG, L’Aquila, Italy, 2 Jun 2004}
    \adcvpresentation{Let’s package GNU/Linux}{Seminari 2004 OpenLUG, L’Aquila, Italy, 26 May 2004}
    \adcvpresentation{Changes in PHP 5/ZendEngine 2.0}{LinuxDay 2003, L’Aquila, Italy, 29 Nov 2003}
    \adcvpresentation{GNU/Linux in practice}{LinuxDay 2002, L’Aquila, Italy, 23 Nov 2002}
  \end{adcvpresentations}
\fi

\end{document}
